### 2016-10-05 Manuscript/SW_early_life_telomeres.Rmd
Edits

#####Early life environment and telomere dynamics
Early-life RTL varied significantly among cohorts (Likelihood ratio test: F = `r round2(anova(lme(RTL~factor(FieldPeriodID),data=juv,random=~1|BirdID))[2,3])`; P `r round3(anova(lme(RTL~Agemonths,data=juv,random=~1|BirdID))[2,4])`). Cohort-level variation in juvenile RTL was not related to adult population density (LMM controlling for age and cohort: t = `r round2(summary(lme(RTL~Agemonths+Density,data=subset(juv,!is.na(Density)),random=~1|FieldPeriodID))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Density,data=subset(juv,!is.na(Density)),random=~1|FieldPeriodID))$tTable[3,5])`), or to temporal variation in  food availability (t = `r round2(summary(lme(RTL~Agemonths+Insect,data=juv,random=~1|FieldPeriodID,na.action=na.exclude))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Insect,data=juv,random=~1|FieldPeriodID,na.action=na.exclude))$tTable[3,5])`).

@@

temp <- dd
temp$y <- ifelse(temp$CqTelomere<15,0,1)

summary(glm(y~Ageclass+Sex+Helper,data=temp,family = 'binomial'))

ggplot(temp,aes(y = RTL,x = Ageclass))+
geom_boxplot()

>>>>

#####Early life environment and telomere dynamics
Early-life RTL varied significantly among cohorts (Likelihood ratio test: F = `r round2(anova(lme(RTL~factor(FieldPeriodID),data=juv,random=~1|BirdID))[2,3])`; P `r round3(anova(lme(RTL~Agemonths,data=juv,random=~1|BirdID))[2,4])`). Cohort-level variation in juvenile RTL was not related to adult population density (LMM controlling for age and cohort: t = `r round2(summary(lme(RTL~Agemonths+Density,data=subset(juv,!is.na(Density)),random=~1|FieldPeriodID))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Density,data=subset(dd,!is.na(Density)),random=~1|BirdID))$tTable[3,5])`), or to temporal variation in  food availability (t = `r round2(summary(lme(RTL~Agemonths+Insect,data=dd,random=~1|BirdID/FieldPeriodID,na.action=na.exclude))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Insect,data=juv,random=~1|BirdID,na.action=na.exclude))$tTable[3,5])`).

@@

temp <- subset(dd,Ageclass !='CH')

ggplot(temp,aes(x = Insect,y = RTL))+
geom_boxplot(aes(group = Insect))+
geom_smooth()+
theme_bw()
